The SMT Competition 2015--2018

### 2019-02-28 2018/report/SMT-COMP.tex
Unique solutions

\paragraph{Further analysis.}

A deeper analysis of the competition results, for example with a view
to improvements in SMT solvers over time, would certainly be
interesting, but goes beyond the immediate mandate of the competition
organizers.  We leave it for future work, noting that all data needed
for such an analysis is publicly available from the competition
website.

>>>>

\subsection{Further Analysis}

Beyond the competition rankings, the competition data provides ample
opportunity for further analysis.  Here, we report on three additional
aspects: progress in solver performance, number of uniquely solved
benchmarks, and use of parallelism in SMT solvers.

\paragraph{Progress in solver performance.}

%TODO

\paragraph{Unique solutions.}

For each SMT solver, the number of uniquely solved benchmarks---that
is, the number of benchmarks that were solved by this solver only---is
a measure of how much the solver contributes to the state-of-the-art,
and the extent to which it is complementary to other solvers.  In
particular, if a solver that uniquely solves~$n$ benchmarks had not
participated in the competition, the virtual best solver would have
been able to solve~$n$ fewer benchmarks.
Table~\ref{table:unique-solutions} shows the number of uniquely solved
benchmarks for each main-track solver from 2015--2018.  (Multiple
versions of a solver are consolidated in this table, and answers that
were given by unsound solver versions are excluded.)

Solvers that rank highly in the competition-wide ranking
(Section~\ref{sec:floc}) often also solve many benchmarks uniquely,
but there are exceptions.  For instance, SMTInterpol has relatively
few unique solutions, despite achieving third place in the
competition-wide ranking in~2017 and~2018.  However, almost every
(sound) solver solves at least some benchmarks uniquely, and hence
contributes to the state-of-the-art.

The largest numbers in Table~\ref{table:unique-solutions} are due to
divisions in which there was only one sound solver: in~2016, MathSAT
was the only solver to support QF\_FP; in~2017, Z3 was the only sound
solver in QF\_FP; and in~2018, CVC4 was the only solver to support
QF\_SLIA, as well as the only sound solver in QF\_ABVFP.  Note that
divisions with fewer than two competing solvers do not affect the
competition-wide ranking.

\begin{table}
  \caption{Number of main-track benchmarks uniquely solved by each
    solver (by year)}
  \label{table:unique-solutions}
  \centering
  \begin{tabular}{lrrrr}
    \toprule
    Solver & 2015 & 2016 & 2017 & 2018 \\
    \midrule
    ABC               &       & 3     &       &        \\
    Alt-Ergo          &       &       &       & 1      \\
    AProVE            & 1     & 0     & 413   & 553    \\
    Boolector         & 37    & 23    & 97    & 62     \\
    COLIBRI           &       &       & 3     & 22     \\
    Ctrl-Ergo         &       &       &       & 12     \\
    CVC3              & 69    &       &       &        \\
    CVC4              & 4884  & 116   & 10258 & 100679 \\
    MapleSTP          &       & 2     &       &        \\
    {[}MathSAT{]}     & 13    & 28748 & 11    & 5      \\
    MinkeyRink        &       & 27    & 27    & 16     \\
    OpenSMT2          & 0     & 0     & 0     & 0      \\
    ProB              &       & 1     &       &        \\
    Q3B               &       & 0     & 89    & 0      \\
    raSAT             & 3     & 14    &       &        \\
    Redlog            &       &       & 4     &        \\
    SMT-RAT           & 13    & 0     & 85    & 2      \\
    SMTInterpol       & 2     & 2     & 5     & 4      \\
    SPASS-SATT        &       &       &       & 34     \\
    STP               & 4     & 2     & 4     & 5      \\
    toysmt            &       & 0     &       &        \\
    Vampire           &       & 139   & 753   & 652    \\
    veriT             & 5     & 21    & 55    & 57     \\
    XSat              &       &       & 0     &        \\
    Yices2            & 88    & 146   & 2379  & 1535   \\
    Z3                & 6139  & 242   & 40992 & 888    \\
    \midrule
    Total             & 11258 & 29486 & 55175 & 104527 \\
    \bottomrule
  \end{tabular}
\end{table}
